### 2015-02-19 fundamentals/intro.tex
moved fcsreqs stuff out of the intro

@@

The \Cyclus paradigm enables targeted contribution and collaboration within the
nuclear fuel cycle analysis community. This essential capability, absent in
previous simulators where user customization and extensibility were not design
objectives, comes about through the \emph{modular and open architecture} of
\Cyclus.  Additionally, \Cyclus facilitates direct comparison of modeling
methodologies with \emph{agent interchangeability}.  Finally, \Cyclus is
applicable to a broader range of fidelities, scales, and applications than
other simulators.  due to the flexibility and generality of its
\emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach}.

Furthermore, modeling the evolution of a physics-dependent, international
nuclear fuel supply chain is a multi-scale problem which existing tools cannot
support. They have either focused on macro effects, e.g., the fleet-level
stocks and flows of commodities, or micro effects, e.g., the used-fuel
composition of fast reactor fuel. Each focus has driven the development of
specialized tools, rendering the task of answering questions between the macro
and micro levels challenging within a single tool.  In contrast, the extensible
architecture and discrete object tracking of \Cyclus allow the creation and
interchangeability of custom archetypes at any level of fidelity.

>>>>

The \Cyclus paradigm enables targeted contribution and collaboration within the
nuclear fuel cycle analysis community. This essential capability is absent in
previous simulators where user customization and extensibility were not design
objectives, and was attained by the \emph{modular and open architecture} of
\Cyclus.  Additionally, \Cyclus facilitates direct comparison of modeling
methodologies with \emph{agent interchangeability}.  Finally, \Cyclus is
applicable to a broader range of fidelities, scales, and applications than
other simulators.  due to the flexibility and generality of its
\emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach}.

Ultimately, modeling the evolution of a physics-dependent, international
nuclear fuel supply chain is a multi-scale problem which existing tools cannot
support. They have either focused on macro effects, e.g., the fleet-level
stocks and flows of commodities, or micro effects, e.g., the used-fuel
composition of fast reactor fuel. Each focus has driven the development of
specialized tools, rendering the task of answering questions between the macro
and micro levels challenging within a single tool.  In contrast, the open, extensible
architecture and discrete object tracking of \Cyclus allow the creation and
interchangeability of custom archetypes at any level of fidelity and by any
fuel cycle analyst.

@@
